### 2022-05-19 project_Luis/paper.tex
test commit
test commit 2
Actualizando anteproyecto

\def\Student{Jesus Rodolfo MORENO CHAVEZ }
\def\Title{MASTERS THESIS PROJECT}
\def\TitleESP{(ANTEPROYECTO)}
\def\Prog{Maestria en Ciencias (F\'{i}sica) }
%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Dept{DIFUS}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Measurement of the Large Hadron Collider luminosity using the CMS silicon pixel detector}
\def\ProjectTitleESP{Medic\'{i}on de la luminosidad del Gran Colisionador de Hadrones usando el detector de pixeles de silicio de CMS}
\def\ResearchLine{Fisica Matematica}

@@

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}
    \\
    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

  This research project consists on the precise determination of the luminosity delivered by the Large Hadron Collider to the Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period  using the Pixel Cluster Counting (PCC) method.
  Luminosity plays a fundamental role in the  measurement of physics processes of elementary particles of the Standard Model, a precise determination of the delivered luminosity allows for precise tests of the Standard Model and searches for new physics.
The PCC method consists of the reconstruction and counting of track clusters produced by charged particle tracks using the Inner Tracker of the CMS detector.
Due to the fine granularity of the pixel sensors of the Inner Tracker, the hit occupancy in the sensors remains very small ($<1\%$) during the proton collisions, this leads to a very linear response and small overall systematic uncertainties for the luminosity measurement.   
  \hspace{2pt}
\vfill

@@

We propose to perform an analysis of the LHC luminosity data recorded by the CMS experiment during 2017 and 2018 using the Pixel Cluster Counting (PCC) method~\cite{LUM12001}.

@@

The main objective of this work is to perform a measurement of the 2017-2018 luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.

@@

As mentioned in the introduction, the precision achieved in the measurement of the integrated luminosity during Run 1 (2011-2012) was about 2.5\% using  methods developed for the first time.
In 2015 and 2016 runs, the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt-corr}.
The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:3}.

@@

\begin{itemize}
\item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent silicon pixel modules.
\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
\item Determine the calibration constant corresponding to the PCC luminometer for proton-proton colisions at 13 TeV using the selected pixel detector components.
\item Determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity for 2017 or 2018 data.
\item Study some of the systematic uncertainties related to the measurement of the luminosity using the PCC. For example, calibration uncertainties, stability, and linearity.
\end{itemize}

@@

The CMS experiment is located at one of the four interaction points of LHC.
The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
A powerful magnet is used to bend charged particles as they move away from the point of collision to identify the charge and measure their momentum.
A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
The electromagnetic calorimeter detects photons and electrons while the hadron calorimeter detects mainly pions and kaons.
The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{fig:CMS}.

@@

\begin{itemize}
\item Final selection of good modules for calculating luminosity using the PCC method.
\item Determination of the PCC calibration constant by analyzing the vdM scan data.
\item Determination of the luminosity per lumi section and integrated for the 2017 or 2018 data.
\item Estimation of the systematic uncertainties associated with the calibration constant or the integrated luminosity values.
\item A presentation of the results in a national or international conference.
\item Publication of the results in a peer-reviewed scientific journal.
\end{itemize}

>>>>

\def\Student{Luis Enrique CUEVAS PICOS }
\def\Title{MASTERS THESIS PROJECT}
\def\TitleESP{(ANTEPROYECTO)}
\def\Prog{Maestria en Ciencias (F\'{i}sica) }
%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Dept{DIFUS}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}
\def\ProjectTitleESP{Desarrollo y calibraci\'{o}n del sistema de medici\'{o}n de luminosidad CMS Silicon Pixel Detector}
\def\ResearchLine{Fisica Matematica}

@@

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}

    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

  This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method, to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
The (PCC) method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
The high densities of pixels of the Inner Tracker gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.   
  \hspace{2pt}
\vfill

@@

We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method. To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.

@@

To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method. To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.

@@

 \cite{Dainese:3}.

@@

\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\end{itemize}

@@

~\ref{fig:CMS}.

@@

\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}
